---
title: "Final Code"
author: "Kate Davey, Emilio Lugo, Mike Ward"
date: '2022-05-01'
output: html_document
---
#Installing Packages
```{r include=FALSE}
source("https://raw.github.com/neilhatfield/STAT461/master/rScripts/checkSetup.R")
checkSetup()
packages <- c("tidyverse", "hasseDiagram", "knitr", "kableExtra", "car", "psych", "parameters", "dplyr",  "DescTools", "emmeans", "openxlsx", "lme4", "nlme", "rstatix", "coin", "rcompanion", "dunn.test", 
  "multcompView")
lapply(packages, library, character.only = TRUE)
options(knitr.kable.NA = "")
options(contrasts = c("contr.sum", "contr.poly"))
source("https://raw.github.com/neilhatfield/STAT461/master/rScripts/ANOVATools.R")

```

#factors
```{r}
GameData<-stat
GameData <- GameData %>%
  dplyr::mutate( 
    Prod.Time = dplyr::recode_factor( 
      Prod.Time, 
      "< 3 years" = "< 3 years",
      "3-5 years" = "3-5 years", 
      ">5 years" = "> 5 years", "> 5 years" = "> 5 years" 
    )
  )

GameData$Genre <- as.factor(GameData$Genre)
GameData$Series <- as.factor(GameData$Series)
GameData$Exclusive <- as.factor(GameData$Exclusive)
GameData$Prod.Time <- as.factor(GameData$Prod.Time)
GameData$Post.Prod <- as.factor(GameData$Post.Prod)
str(GameData)
```

#Visualizations
```{r}
ggplot( 
  data = GameData, 
  mapping = aes( 
    x = Prod.Time, 
    y = Num_Copies, 
  ) 
) + 
  geom_boxplot() + 
  theme_bw() + 
  xlab("Production Time") + 
  ylab("Number of Copies (in Millions)") + 
  theme( 
    legend.position = "right",
    text = element_text(size = 14,)
  )+
  labs(title = ("Box Plot of Game Data"))
```

#Descriptive Statistics

```{r}
GameStats <- psych::describeBy(
  x = GameData$Num_Copies, # Notice how we're getting the factorial treatments 
  group = paste(GameData$Prod.Time, sep = " x "), 
  na.rm = TRUE, 
  skew = TRUE, 
  ranges = TRUE, 
  quant = c(0.25, 0.75),
  IQR = TRUE, 
  mat = TRUE, 
  digits = 4
)

GameStats %>% 
  tibble::remove_rownames() %>%
  tibble::column_to_rownames(
    var = "group1" 
  ) %>% 
  dplyr::select(
    n, min, Q0.25, median, Q0.75, max, mad, mean, sd, skew, kurtosis 
  ) %>% 
  knitr::kable(
    caption = "Summary Statistics for Game Data",
    digits = 3,
    format.args = list(big.mark = ","),
    align = rep('c', 11),
    col.names = c("n", "Min", "Q1", "Median", "Q3", "Max", "MAD", "SAM", "SASD", "Sample Skew","Sample Ex. Kurtosis"),
    booktabs = TRUE 
  ) %>% 
  kableExtra::kable_styling(
    font_size = 12,
    latex_options = c("HOLD_position", "scale_down") 
  )
```
# Base Interaction Plot
```{r}
interaction.plot(
  x.factor = GameData$Prod.Time, # First Factor 
  trace.factor = GameData$Post.Prod, # Second Factor
  response = GameData$Num_Copies, # Response fun = mean, 
  type = "b", # Both points and lines 
  col = c("black","red","blue"), # Set colors for trace 
  pch = c(19, 17, 15), # Set symbols for trace 
  fixed = TRUE, legend = TRUE, 
  xlab = "Production Time",
  ylab = "Number of Copies (in Millions)",
  main = "Interaction Plot of Game Data",
  trace.label = "Post Production",
)
```
###Simple Model
```{r}
GameModelA <- aov(
  formula = Num_Copies ~ Prod.Time, 
  data = GameData
)
tempA <- car::boxCox(GameModelA)
tempA$x[which(tempA$y == max(tempA$y))]
SGM <- psych::geometric.mean(GameData$Num_Copies)
GameData <- GameData %>%
  mutate(
    AZSales = (Num_Copies^0.25 - 1)/(0.25 * SGM^(0.25-1))
  )
GameModelZ <- aov(
  formula = AZSales ~ Prod.Time, 
  data = GameData)
```

#Q-Q Plot For Simple Model
```{r}
car::qqPlot( 
  x = residuals(GameModelZ),
  distribution = "norm",
  envelope = 0.9, 
  id = FALSE, 
  pch =20, 
  ylab = "Residuals (Num_Copies sold in millions)",
  main = "Q-Q Plot for Simple Model"
)
```
#Homoscedasticity For Simple Model
```{r}
plot(GameModelZ, which = 1)
```
#ANOVA For Simple Model
```{r}
parameters::model_parameters( 
  model = GameModelZ,
  omega_squared = "raw", # Notice the use of partial
  eta_squared = "raw", 
  epsilon_squared = "raw", 
  type = 3, # Use 1, 2, or 3 for the Type of SSQs you want 
  drop = "(Intercept)", # Drop an unneeded row for ANOVA
  verbose = FALSE # Makes the function "quiet" 
) %>% 
  knitr::kable(
    digits = 4, 
    col.names = c("Source", "SS", "df", "MS", "F", "p-value", "Omega Sq.", "Eta Sq.", "Epsilon Sq."),
    caption = "ANOVA Table for Game Data Simple Model", 
    align = c('l',rep('c',8)),
    booktab = TRUE 
  ) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("striped", "condensed"),
    font_size = 12, 
    latex_options = c("scale_down", "HOLD_position") 
  )
```

#Point Estimates For Simple Model
```{r}
pointZEst <- dummy.coef(GameModelZ)
pointZEst <- unlist(pointZEst)
names(pointZEst) <- c("Grand Mean", 
                      levels(GameData$Prod.Time))
data.frame("est" = pointZEst) %>%
  mutate(
    untransEst = (est * 0.25 * SGM^(0.25 - 1) + 1)^(1/0.25)
  ) %>%
  knitr::kable( 
    digits = 2, 
    col.names = c("Box-Cox Estimate", "Untransformed Estimate"),
    caption = "Point Estimates For Simple Model", 
    booktabs = TRUE, align = "c" 
  ) %>%
  kableExtra::kable_styling(
    font_size = 12,
    latex_options = c("HOLD_position") 
  )
```

#Complex Model
```{r}
GameModelN <- aov(
  formula = Num_Copies ~ Prod.Time + Post.Prod + Series + Genre + Exclusive + Prod.Time, 
  data = GameData
  )
temp1 <- car::boxCox(GameModelN)
temp1$x[which(temp1$y == max(temp1$y))]

SGM <- psych::geometric.mean(GameData$Num_Copies)

GameData <- GameData %>%
  mutate(
    bcSales = (Num_Copies^0.25 - 1)/(0.25 * SGM^(0.25-1))
  )

GameModelBC <- aov(
  formula = bcSales ~ Prod.Time + Post.Prod + Series + Genre + Exclusive + Post.Prod:Exclusive, 
  data = GameData)
```
#Gaussian For Complex Model
```{r}
car::qqPlot( 
  x = residuals(GameModelBC),
  distribution = "norm",
  envelope = 0.9, 
  id = FALSE, 
  pch =20, 
  ylab = "Residuals (Number of Copies Sold in Millions)", 
  main = "Q-Q Plot for Complex Model"
)
```

#Homoscedasticity For Complex Model
```{r}
ggplot( 
  data = data.frame( 
    residuals = residuals(GameModelBC), 
    fitted = fitted.values(GameModelBC) 
  ), 
  mapping = aes(x = fitted, y = residuals) 
) + 
  geom_point(size = 2) + 
  geom_hline(
    yintercept = 0, 
    linetype = "dashed",
    color = "grey50" 
  ) + 
  geom_smooth( 
    formula = y ~ x,
    method = stats::loess, 
    method.args = list(degree = 1), 
    se = FALSE, 
    size = 0.5 
  ) + 
  theme_bw() + 
  xlab("Fitted values (Num_Copies sold in millions)") + 
  ylab("Residuals (Num_Copies sold in millions)")+ 
  labs(title = "Scatterplot for Complex Model")
```
# Omnibus Test/Modern ANOVA Table for Complex Model
```{r}
parameters::model_parameters( 
  model = GameModelBC,
  omega_squared = "partial", # Notice the use of partial
  eta_squared = "partial", 
  epsilon_squared = "partial", 
  type = 3, # Use 1, 2, or 3 for the Type of SSQs you want 
  drop = "(Intercept)", # Drop an unneeded row for ANOVA
  verbose = FALSE # Makes the function "quiet" 
) %>% 
  dplyr::mutate(
    p = ifelse( 
      test = is.na(p),
      yes = NA, 
      no = pvalRound(p) 
    ) 
  ) %>%
  knitr::kable(
    digits = 4, 
    col.names = c("Source", "SS", "df", "MS", "F", "p-value", "Partial Omega Sq.", "Partial Eta Sq.", "Partial Epsilon Sq."),
    caption = "ANOVA Table for Complex Model", 
    align = c('l',rep('c',8)),
    booktab = TRUE 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("striped", "condensed"),
    font_size = 12, 
    latex_options = c("scale_down", "HOLD_position") 
  )
```
# Point Estimates for Complex Model
```{r}
pointEst <- dummy.coef(GameModelBC) 
pointEst <- unlist(pointEst) 
names(pointEst) <- c(
  "Grand Mean", 
  paste("Production Time:",levels(GameData$Prod.Time)),
  paste("Post Production:",levels(GameData$Post.Prod)),
  paste("Series:", levels(GameData$Series)), 
  paste("Genre:", levels(GameData$Genre)), 
  paste("Exclusive:", levels(GameData$Exclusive)),
  paste("Post Production and Exclusive:", c("no & no", "yes & no", "no & yes", "yes & yes"))
)
data.frame("est" = pointEst) %>%
  mutate(
    untransEst = (est * 0.25 * SGM^(0.25 - 1) + 1)^(1/0.25)
  ) %>%
  knitr::kable( 
    digits = 2, 
    col.names = c("Box-Cox Estimate", "Untransformed Estimate"),
    caption = "Point Estimates For Complex Model", 
    booktabs = TRUE, align = "c" 
  ) %>%
  kableExtra::kable_styling(
    font_size = 12,
    latex_options = c("HOLD_position") 
  )
```
## Kable Code for Newman Keuls For Complex Model

```{r}
dtPH <- DescTools::PostHocTest(
  x = GameModelBC, # Your aov/lm object
  method = "newmankeuls", # Your chosen method
  conf.level = 0.9 # 1 -- Your Overall Type I Error Rate 
)
```
## Kable Code for DescTools

```{r}
a <- knitr::kable(
  x = dtPH$Prod.Time, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Production time Post Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
a
```
```{r}
b <- knitr::kable(
  x = dtPH$Post.Prod, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Post Production Post Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
b
```
```{r}
c <- knitr::kable(
  x = dtPH$Series, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Series Post Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
c
```
```{r}
d <- knitr::kable(
  x = dtPH$Genre, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Post.Prod Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
d
```
```{r}
e<- knitr::kable(
  x = dtPH$Exclusive, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Exclusive Post Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
e
```

```{r}
f<- knitr::kable(
  x = dtPH$`Post.Prod:Exclusive`, # Notice the use of the factor name
  digits = 3,
  caption = paste( # Creates a nice title; copy at will
  "Post Production X Exclusive Post Hoc",
  attr(dtPH, "method"),
  "Comparisons" ),
  col.names = c("Difference", "Lower Bound", "Upper Bound",         "Adj. p-Value"), 
  align = 'lcccc', booktabs = TRUE, 
) %>% 
  kableExtra::kable_styling( 
    bootstrap_options = c("condensed", "boardered"), 
    font_size = 12, 
    latex_options = "HOLD_position"
  )
f
```
#Comparisons For Complex Model
```{r}
example1 <- emmeans::emmeans(
  object = GameModelBC,
  specs = pairwise ~ Prod.Time | Genre,
  adjust = "fdr",
  level = 0.90
)

as.data.frame(example1$contrasts) %>%
knitr::kable(
digits = 4,
 col.names = c("Production Times", "Genre", "Estimate","SE", "DF",
 "t Statistic", "p-value"),
caption = "Conditional Pairwise Comparisons for Complex Model",
align = rep("c", 7),
booktabs = TRUE,
longtable = TRUE
) %>%
kableExtra::kable_styling(
bootstrap_options = c("striped", "condensed"),
font_size = 12,
latex_options = c("HOLD_position", "repeat_header")
)
```

